---
title: "Homework_7_badplot_goodplot_analysis"
author: "Theresa Jones"
date: "10/4/2021"
output: github_document
---

``````{r, message=FALSE, warning=FALSE, eval=TRUE}
library(tidyverse)
data("iris")
```

```{r BadPlot}
petals.n.sepals <- ggplot(data=iris, mapping=aes(x= Sepal.Length, y= Petal.Length))+
         geom_point()

petals.n.sepals + 
  xlab(NULL) + 
  ylab(NULL)

petals_n_sepals_bad
```

A problem with this plot is the missing axis titles. This goes against the princple of graphical integrity that covers clear labeling of the graph and the data, and is discussed better in section 22.2 of the data visualization guide by Wilke. The lack of axis labels does not give the reader/viewer any sense of the context of the relationship displayed on the plot. There is also no type of legend to define what the datapoints might be, so while there is a positive correlation shown, there is no information as to what there is a correlation between. The units of measurement for the quantities shown on the graph, so again we cannot be sure that we are using the best range for our data, since we do not have any context to make an assumption of the data making sense.


```{r, GoodPlot}
ggplot(data=iris, mapping=aes(x= Sepal.Length, y= Petal.Length, colour= Species))+
         geom_point()+
         ggtitle("Petal and Sepal Lengths by Iris Species")+
  labs(y= " Petal Length (cm)", x = "Sepal Length (cm)")

petals_n_sepals_good
```

This would be a better plot simply with the axis titles and a graph title. We now have an idea of what this positive correlation is between two (previously) unknown variables. We can see a clear relationship between petal and sepal length of irises of different species. The difference in color of the datapoints between species is also a useful addition to this plot as well because this adds another layer to our understanding of the data without adding another piece of information to the data. Without the species-specific color points, one may think to change the format into something like a bar graph, where the petal and sepal lengths might be separated by species. A linear relationship wouldn't be very easy spot in that format, taking away the opportunity for an easy to spot trend in the data. Here we provide context with efficient use of data ink already being used. The efficient use of data ink on a plot is important for the overall effectiveness and readability of the data as discussed in Tufte ch. 4. 

